The development of infants' responses to mispronunciations - A Meta-Analysis

### 2018-12-03 Paper_Analyses.tex
addressed comments by Christina; started on General Discussion

\linenumbers

@@

{[}Christina: changed concepts to mechanisms in the next paragraph,
because I want to refer to what they represent, but I am not sure it's
the right term{]}{[}Katie: Karen (Mulak) talks about these terms as
concepts. Mechanisms to me means some sort of internalization, that they
would have had this ability all along and just need to apply it. It
could be that we fundamentally disagree on this, but to me these are
things that infants discover. Later on we use principles. What about
\enquote{principles that infants must discover}\ldots{} \enquote{in
order to form adult-like word representations}? I took away
\enquote{which are both present in the mature language processing
system}.{]} {[}Christina: I like principles. This is then good for
me.{]}

@@

{[}Katie: since we actually don't have theoretical framework support for
the no-change theory, I've changed around the sentence below to
explicitly say that only 2 of the 3 are predicted by theoretical
accounts.{]}{[}Christina: Works for me. I am just thinking what the
Vihman-style framework says. do you happen to know? I think the Renner
thesis discusses it.{]}

@@

The present meta-analysis was conducted with maximal transparency and
reproducibility in mind. To this end, we provide all data and analysis
scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
2014). The most recent version is available via the website and the
interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
2018). Since the present paper was written with embedded analysis
scripts in R {[}@R, @RMarkdown, @papaja{]}, it is always possible to
re-analyze an updated dataset. In addition, we follow the Preferred
Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
guidelines and make the corresponding information available as
supplementary materials (Moher, Liberati, Tetzlaff, Altman \&
PRISMAGroup, 2009). Figure X plots our PRISMA flowchart illustrating the
paper selection procedure.

{[}Figure X. PRISMA Flowchart.{]}
(figures/PRISMA\_MA\_Mispronunciation.png)

@@

The 34 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
2014; Bergmann et al., 2018). For each experiment (note that a paper
typically has multiple experiments), we entered variables describing the
publication, population, experiment design and stimuli, and results. For
the analyses presented in this section, we focus on the following
characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 271 records in our data.

@@

We report effect sizes for infants' looks to target pictures after
hearing a correctly pronounced or a mispronounced label (object
identification) as well as the difference between effect sizes for
correct and mispronounced trials (i.e.~mispronunciation sensitivity).
The effect size we report in the present paper are based on comparison
of means, standardized by their variance. The most well-known effect
size from this group is Cohen's \emph{d} {[}@cohen{]}. To correct for
the small sample sizes common in infant research, however, we use as a
dependent variable Hedges' \emph{g} instead of Cohen's \emph{d} (Hedges,
1981; Morris, 2000).

{[}Christina{]} These numbers seem wrong! Again, how about (xx effect
sizes from yy papers)? {[}Katie{]} Well, they are kind of wrong :) Two
papers report both for different experimental conditions. I've given the
explanation now, not sure if that is good enough, but I'm really not
sure how to say it a different way. {[}Katie{]} Do you want number of
records and papers for the imputed correlations as well? You've put a
-1, assuming there was something wrong with one of the papers or
something like that? How does that shake out for number of records?
{[}Christina: No clue what the -1 was, sorry.{]}

We calculate Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 186 records from 26 papers)
or using reported t-values (\emph{n} = 74 records from 9 papers). Two
papers reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
standard deviations were extracted from figures for 4 papers. In a
within-participation design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance based on t-values. Upon request we
were provided with correlation values for one paper (Altvater-Mackensen,
2010); we were able to compute correlations using means, standard
deviations, and t-values for \emph{n} = 5 (following Csibra, et al.
2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
Correlations were imputed for the remaining papers (see Black \&
Bergmann, 2017, for the same procedure). For two papers, we could not
derive any effect size (Ballem \& Plunkett, Renner), and for a third
paper, we do not have sufficient information in one record to compute
effect sizes (Skoruppa). We compute a total of 106 effect sizes for
correct pronunciations and 150 for mispronunciations. Following standard
meta-analytic practice, we remove outliers, i.e.~effect sizes more than
3 standard deviations from the respective mean effect size. This leads
to the exclusion of 2 records for correct pronunciations and 3 records
for mispronunciations.

@@

{[}Christina: In the above 2 paragraphs I got confused, should it be
present or past. I think it switched in the las tparagraph so I started
to adapt, but I think it would be best for you to decide. {]}

@@

In the psychological sciences, there is a documented reluctance to
publish null results. As a result, significant results tend to be
over-reported and thus might be over-represented in our meta-analyses
(see Ferguson \& Heene, 2012). To examine whether this is also the case
in the mispronunciation sensitivity literature, which would bias the
data analyzed in this meta-analysis, we conduct two tests. We first
examine whether effect sizes are distributed as expected based on
sampling error using the rank correlation test of funnel plot asymmetry
with the R {[}@R{]} package metafor {[}@metafor{]}. Effect sizes with
low variance are expected to fall closer to the estimated mean, while
effect sizes with high variance should show an increased,
evenly-distributed spread around the estimated mean. Publication bias
would lead to an uneven spread.

Second, we analyze all of the significant results in the dataset using a
p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve
tests for evidential value by examining whether the p-values follow the
expected distribution of a right skew in case the alternative hypothesis
is true, versus a flat distribution that speaks for no effect being
present in the population and all observed significant effects being
spurious. Responses to correctly pronounced and mispronounced labels are
predicted to show different patterns of looking behavior. In other
words, there is an expectation that infants should look to the target
when hearing a correct pronunciation, but studies vary in their report
of significant looks to the target when hearing a mispronounced label
(i.e.~there might be no effect present in the population, see e.g., );
as a result, we conduct these two analyses to assess publication bias
separately for both conditions.

@@

The models reported here are hierarchical random-effects models (infant
groups nested within papers) of variance-weighted effect sizes, which we
computed with the R {[}@R{]} package metafor {[}@metafor{]}. To
investigate how development impacts mispronunciation sensitivity, our
core theoretical question, we introduce age (centered; continuous and
measured in days but transformed into months for ease of interpreting
estimates by dividing by 30.44) as a moderator to our main model. For a
subsequent exploratory investigations of experimental characteristics,
we introduce each characteristic as a moderator (more detail below).

@@

{[}Chrisitna: If you add prisma, then this is figure 2{]}

Figure 1 shows the funnel plots for both correct pronunciations and
mispronunciations (code adapted from Sakaluk, 2016). Funnel plot
assymmetry was significant for both correct pronunciations (Kendall's
\(\tau\) = 0.53, \emph{p} \textless{} .001) and mispronunciations
(Kendall's \(\tau\) = 0.16, \emph{p} = 0.004). These results,
quantifying the assymmetry in the funnel plots (Figure 1), indicate bias
in the literature. This is particularly evident for correct
pronunciations, where larger effect sizes have greater variance (bottom
right corner) and there are a smaller number of more precise effect
sizes (i.e.~smaller variance) than expected (top left, outside the
triangle).

@@

We should also point out that funnel plot asymmetry can be caused by
multiple factors beside publication bias. The funnel plot asymmetry may
also reflect heterogeneity in the data. There are various possible
sources of heterogeneity, which our subsequent moderator analyses will
begin to address. Nonetheless, we will remain cautious in our
interpretation of our findings and hope that an open dataset that can be
expanded by the community will attract previously unpublished null
results so we can better understand infants' developing mispronunciation
sensitivity.

\subsection{(Insert Figure 1 about
here)}\label{insert-figure-1-about-here}

@@

We first calculated the meta-analytic effect for infants' ability to
identify objects when hearing correctly pronounced labels. The
variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.908
(SE = 0.12) which was significantly different from zero (CI {[}0.673,
1.143{]}, \emph{p} \textless{} .001). This is a rather large effect size
(according to the criteria set by Cohen, 1988; see also Bergmann, et
al., 2018; for comparative meta-analytic effect sizes in language
acquisition research). That the effect size is significantly above zero
suggests that when presented with the correctly pronounced label,
infants fixated the corresponding object. Our analysis of funnel plot
asymmetry, however, found evidence for publication bias, which might
lead to an overestimated effect sizes as smaller, non-significant
results might not be published despite the fact that they should occur
regularly even in well-powered studies. Although the effect size Hedges'
\emph{g} may be overestimated for object identification in response to
correctly pronounced words, the p-curve results and a CI lower bound of
0.67 which is substantially above zero suggests that this result should
be robust even when correcting for publication bias. In other words, we
are confident that the true population mean lies above zero for object
recognition of correctly pronounced words.

@@

{[}Christina{]} I am not sure about the placement of this paragraph
because the next section cannot explain this heterogeneity, so maybe we
should move it down to the beginning of the age part? {[}Katie{]} I
think that makes sense, moving it!

@@

The above two analyses considered the data from mispronounced and
correctly pronounced words separately. To evaluate mispronunciation
sensitivity, we compared the effect size Hedges' \emph{g} for correct
pronunciations with mispronunciations directly. To this end, we combined
the two datasets. The moderator test was significant, QM(1) = 215.761,
\emph{p}\textless{} .001. The estimate for mispronunciation sensitivity
was 0.495 (SE = 0.034), and infants' looking times across conditions
were significantly different (CI {[}0.429, 0.561{]}, \emph{p}
\textless{} .001). This confirms that although infants fixate the
correct object for both correct pronunciations and mispronunciations,
the observed fixations to target (as measured by the effect sizes) were
significantly greater for correct pronunciations. In other words, we
observe a significant difference between the two conditions and can now
quantify the modulation of fixation behavior in terms of standardized
effect sizes and their variance. This first result has both theoretical
and practical implications, as we can now reason about the amount of
perturbance caused by mispronunciations and can plan future studies to
further investigate this effect with suitable power.

@@

To evaluate the different predictions we laid out in the introduction
for how mispronunciation sensitivity will change as infants develop, we
next added the moderator age (centered; continuous and measured in days
but transformed into months for ease of interpreting estimates by
dividing by 30.44 for Figure 2). {[}Christina{]} What about the whole
months thing? {[}Katie{]} We had an explanation in the methods section
for this, I've now added it again here.

In the first analyses, we investigate the impact of age separately on
conditions where words were either pronounced correctly or not. Age did
not significantly modulate object identification in response to
correctly pronounced (QM(1) = 0.678, \emph{p}= 0.41) or mispronounced
words (QM(1) = 1.715, \emph{p}= 0.19). The lack of a significant
modulation together with the small estimates (correct: \(\beta\) =
0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p}= 0.41;
mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.007,
0.037{]}, \emph{p}= 0.19) indicates that there was no relationship
between age and target looks in response to a correctly pronounced or
mispronounced label. We plot both object recognition and
mispronunciation sensitivity as a function of age in Figure 2.

{[}Christina{]} OK there is a mismatch between what you write and the
numbers, can you verify? {[}Katie{]} Good catch. For some reason, it was
just copying over the moderator test from mispronunciation sensitivity,
even though I was calling for the age moderator analysis. There is no
significant moderator test, but it was just pasting the same one again
and again. I've fixed my code, so it should be correct now!

We then examined the interaction between age and mispronunciation
sensitivity (correct vs.~mispronounced words) in our whole dataset. The
moderator test was significant (QM(3) = 218.621, \emph{p}\textless{}
.001). The interaction between age and mispronunciation sensitivity,
however, was not significant (\(\beta\) = 0.003, SE = 0.008, 95\%
CI{[}-0.012, 0.018{]}, \emph{p}= 0.731), pointing to the moderator test
being driven by the difference between conditions. The small estimate,
as well as inspection of Figure 2 suggests that as infants age, their
mispronunciation sensitivity remains the same.

@@

Of the 32 papers included in the meta-analysis, 13 analyzed the
relationship between vocabulary scores and object recognition for
correct pronunciations and mispronunciations (comprehension = 11 papers
and 39 records; production = 3 papers and 20 records). There is reason
to believe that production data are different from comprehension data
(the former being easier to estimate for parents in the typical
questionnaire-based assessment; Kidd citation), and we therefore planned
to analyze these two types of vocabulary measurement separately.
However, only 3 papers reported correlations with productive vocabulary
scores, limiting the conclusions that can be drawn. In our vocabulary
analysis, we therefore focus exclusively on the relationship between
comprehension and mispronunciation sensitivity.

{[}Christina{]} Removed the previous comment chaos. So can you not only
list papers but also n conditions above? With just 1 paper for
production, I wouldn't analyze it to be honest. it's just not enough
data. I also liked your comments about the time line of this whole
thing, can you extract the years of papers which report this? Might be
extremely useful in the discussion and strengthens our case that there
is no effect, bc people don't find the predicted relation with vocab.
Also, cann you add a citation for comp vs prod? I think Evan Kidd had a
paper on it, if you don't have one handy, I can look it up. {[}Katie{]}
I couldn't find what you are referring to. Could you add the Evan Kidd
paper? Also, I added a histogram figure below, but I'm not so very sure
that it is good enough to add to the paper (its under the heading
\enquote{Potential Vocabulary Figure}). Let me know what you think.

We first considered the relationship between vocabulary and object
recognition for correct pronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 9 of 10 experimental conditions, with correlation
values ranging from -0.16 to 0.48. The mean effect size Pearson's
\emph{r} of 0.14 was small and did not differ significantly from zero
(CI {[}0.03; 0.25{]} \emph{p} = 0.012). However, the lower bound of the
CI is close to zero, and one might hypothesize that with more power the
small relationship might become significant. At the same time, a larger
sample might confirm our conclusion that there is no relationship. As a
result, we can not draw firm conclusions about the relationship between
comprehension scores and object recognition in response to correct
pronunciations.

We next considered the relationship between vocabulary and object
recognition for mispronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 17 of 29 experimental conditions, with correlation
values ranging from -0.35 to 0.57. The mean effect size Pearson's
\emph{r} of 0.05 was small and did not differ significantly from zero
(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). Similar to the relationship
between comprehension scores and correct pronunciation object
identification, the small correlations and large variances suggest a
lack of relationship between vocabulary and object recognition for
mispronunciations. We again emphasize that we cannot draw firm
conclusions due to the small number of studies we were able to include
here.

\subsection{Potential Vocabulary
Figure}\label{potential-vocabulary-figure}

@@

{[}Christina{]} This section talked about several variables in 2
categories, but in reality there are only 2 variables, right? I am not
100\% sure about total trial length as being the first or being
mentioned at all, might it be better to focus on time window analyzed
and then say \enquote{Oh, btw, total trial length totally does nothing
so we don't have to discuss it further} I am not sure, so feel free to
re-rewrite this, but now it better lines up with everything before
because trial length kinda comes out of nowhere. {[}Katie{]} That's
fair! I think we don't need the full analysis for total time presented,
but I'd like to still mention all of them because it really shows that
its something about this post-naming time window choice that influences
it, and not just fishing around for variability until we find something
that works. In the end there are 2 interesting analyses, but offset
could have been interesting (but wasn't). Therefore, I'd still like to
refer to the timing variables as a type of category. Otherwise, we say
we'll do size of time window analyzed, but then we have information
about other timing stuff as well.

@@

{[}Christina{]} Is there a reason you choose mode and not median?
{[}Katie{]} Hmm, I felt like mode would be interesting, because it gives
the most popular choice (74 experimental conditions). But, the median is
only 500 ms less, so we could use that too (9 experimental conditions).

{[}Christina{]} Would it make sense to present dependent variable first?
{[}Katie{]} I don't have a strong opinion on this. If you think it would
be better, then I can change it.

In a typical trial in a mispronunciation sensitivity study, the
target-distractor image pairs are first presented in silence, followed
by auditory presentation of a carrier phrase or isolated presentation of
the target word (correctly pronounced or mispronounced). When designing
mispronunciation sensitivity studies, experimenters can choose the
length of time each trial is presented. This includes both the length of
time before the target object is named (pre-naming phase) as well as
after (post-naming phase) and is determined prior to data collection. To
examine the size of the time window analyzed in the post-naming phase,
we must first consider overall length of time post-naming, because it
limits the overall time window available to analyze and might thus
predict which time window was analyzed. Across papers, actual
post-naming phase length varied from 2000 to 9000 ms, with a median
value of 3500 ms. There was an inverse relationship between infant age
and actual post-naming phase length, such that younger infants were
presented with longer a longer post-naming phase, although this
correlation was not significant (\emph{r} = 0.01, \emph{p} = 0.882).
Presumably, younger infants may be exposed to longer trials because
their word recognition abilities are expected to be slower than older
infants (Fernald et al., 1998).

Unlike the actual post-naming phase length, the size of the post-naming
time window analyzed can be chosen after the experimental data is
collected. Interestingly, half of the experimental conditions were
analyzed using the same length of post-naming phase as the infant heard
in the actual experiment (124), while the other half were analyzed using
a shorter length of post-naming phase, excluding later portions of the
post-naming phase (127). Across papers, the length of the post-naming
phase analyzed varied from 1510 to 4000 ms, with a median value of 2500
ms. Similar to actual post-naming phase length, there was an inverse
relationship between infant age and the size of the post-naming time
window analyzed, such that younger infants' looking times were analyzed
using a longer post-naming time window, here the relationship was
significant (\emph{r} = -0.23, \emph{p} \textless{} .001). Again, the
choice to analyze a shorter post-naming time window is likely related to
evidence that speed of processing is slower in younger infants (Fernald
et al., 1998). To summarize, we observe variation in time-related
aspects related to infants' age. This variation is most pronounced, and
even significant, for the time window that is being analyzed after the
target label has been heard.

>>>>

\linenumbers
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\AtBeginEnvironment{tablenotes}{\doublespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1.5}}

@@

@@

{[}Katie: since we actually don't have theoretical framework support for
the no-change theory, I've changed around the sentence below to
explicitly say that only 2 of the 3 are predicted by theoretical
accounts.{]}{[}Christina: Works for me. I am just thinking what the
Vihman-style framework says. do you happen to know? I think the Renner
thesis discusses it.{]} {[}Katie: I wasn't really familiar with the
Vihman framework, but looking at Renner's thesis and some of the
original papers suggests that it really is about production, not
perception.{]}

@@

The present meta-analysis was conducted with maximal transparency and
reproducibility in mind. To this end, we provide all data and analysis
scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
2014). The most recent version is available via the website and the
interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
2018). Since the present paper was written with embedded analysis
scripts in R {[}@R, @RMarkdown, @papaja{]}, it is always possible to
re-analyze an updated dataset. In addition, we followed the Preferred
Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
guidelines and make the corresponding information available as
supplementary materials (Moher, Liberati, Tetzlaff, Altman \&
PRISMAGroup, 2009). Figure 1 plots our PRISMA flowchart illustrating the
paper selection procedure.

\begin{figure}
\centering
\includegraphics{figures/PRISMA_MA_Mispronunciation.png}
\caption{}
\end{figure}

@@

The 32 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
2014; Bergmann et al., 2018). For each experiment (note that a paper
typically has multiple experiments), we entered variables describing the
publication, population, experiment design and stimuli, and results. For
the planned analyses to evaluate the development of mispronunciation
sensitivity, we focus on the following characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 260 records in our data.

@@

Effect sizes are reported for infants' looks to target pictures after
hearing a correctly pronounced or a mispronounced label (object
identification) as well as the difference between effect sizes for
correct and mispronounced trials (i.e.~mispronunciation sensitivity).
The effect size reported in the present paper is based on comparison of
means, standardized by their variance. The most well-known effect size
from this group is Cohen's \emph{d} {[}@cohen{]}. To correct for the
small sample sizes common in infant research, however, we used as a
dependent variable Hedges' \emph{g} instead of Cohen's \emph{d} (Hedges,
1981; Morris, 2000).

{[}Katie{]} Do you want number of records and papers for the imputed
correlations as well? You've put a -1, assuming there was something
wrong with one of the papers or something like that? How does that shake
out for number of records? {[}Christina: No clue what the -1 was,
sorry.{]}

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 186 records from 26 papers)
or using reported t-values (\emph{n} = 74 records from 9 papers). Two
papers reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
standard deviations were extracted from figures for 3 papers. In a
within-participation design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance based on t-values. Upon request we
were provided with correlation values for one paper (Altvater-Mackensen,
2010); we were able to compute correlations using means, standard
deviations, and t-values for \emph{n} = 5 (following Csibra, et al.
2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
Correlations were imputed for the remaining papers (see Black \&
Bergmann, 2017, for the same procedure). For two papers, we could not
derive any effect size (Ballem \& Plunkett, Renner), and for a third
paper, we do not have sufficient information in one record to compute
effect sizes (Skoruppa). We compute a total of 106 effect sizes for
correct pronunciations and 150 for mispronunciations. Following standard
meta-analytic practice, we remove outliers, i.e.~effect sizes more than
3 standard deviations from the respective mean effect size. This leads
to the exclusion of 2 records for correct pronunciations and 3 records
for mispronunciations.

@@

{[}Christina: In the above 2 paragraphs I got confused, should it be
present or past. I think it switched in the las tparagraph so I started
to adapt, but I think it would be best for you to decide. {]}{[}Katie:
Good catch. I've gone through the Methods section and changed everything
to past, per APA guidelines.{]}

@@

In the psychological sciences, there is a documented reluctance to
publish null results. As a result, significant results tend to be
over-reported and thus might be over-represented in our meta-analyses
(see Ferguson \& Heene, 2012). To examine whether this is also the case
in the mispronunciation sensitivity literature, which would bias the
data analyzed in this meta-analysis, we conducted two tests. We first
examined whether effect sizes are distributed as expected based on
sampling error using the rank correlation test of funnel plot asymmetry
with the R {[}@R{]} package metafor {[}@metafor{]}. Effect sizes with
low variance were expected to fall closer to the estimated mean, while
effect sizes with high variance should show an increased,
evenly-distributed spread around the estimated mean. Publication bias
would lead to an uneven spread.

Second, we analyze all of the significant results in the dataset using a
p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve
tests for evidential value by examining whether the p-values follow the
expected distribution of a right skew in case the alternative hypothesis
is true, versus a flat distribution that speaks for no effect being
present in the population and all observed significant effects being
spurious. Responses to correctly pronounced and mispronounced labels
were predicted to show different patterns of looking behavior. In other
words, there is an expectation that infants should look to the target
when hearing a correct pronunciation, but studies vary in their report
of significant looks to the target when hearing a mispronounced label
(i.e.~there might be no effect present in the population, see e.g., );
as a result, we conducted these two analyses to assess publication bias
separately for both conditions.

@@

The models reported here are hierarchical random-effects models (infant
groups nested within papers) of variance-weighted effect sizes, which we
computed with the R {[}@R{]} package metafor {[}@metafor{]}. To
investigate how development impacts mispronunciation sensitivity, our
core theoretical question, we introduced age (centered; continuous and
measured in days but transformed into months for ease of interpreting
estimates by dividing by 30.44) as a moderator to our main model. For a
subsequent exploratory investigations of experimental characteristics,
we introduced each characteristic as a moderator (more detail below).

@@

Figure 2 shows the funnel plots for both correct pronunciations and
mispronunciations (code adapted from Sakaluk, 2016). Funnel plot
assymmetry was significant for both correct pronunciations (Kendall's
\(\tau\) = 0.53, \emph{p} \textless{} .001) and mispronunciations
(Kendall's \(\tau\) = 0.16, \emph{p} = 0.004). These results,
quantifying the assymmetry in the funnel plots (Figure 1), indicate bias
in the literature. This is particularly evident for correct
pronunciations, where larger effect sizes have greater variance (bottom
right corner) and there are a smaller number of more precise effect
sizes (i.e.~smaller variance) than expected (top left, outside the
triangle).

@@

We should also point out that funnel plot asymmetry can be caused by
multiple factors beside publication bias, such as heterogeneity in the
data. There are various possible sources of heterogeneity, which our
subsequent moderator analyses will begin to address. Nonetheless, we
will remain cautious in our interpretation of our findings and hope that
an open dataset which can be expanded by the community will attract
previously unpublished null results so we can better understand infants'
developing mispronunciation sensitivity.

\subsection{(Insert Figure 2 about
here)}\label{insert-figure-2-about-here-1}

@@

We first calculated the meta-analytic effect for infants' ability to
identify objects when hearing correctly pronounced labels. The
variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.908
(SE = 0.12) which was significantly different from zero (CI {[}0.673,
1.143{]}, \emph{p} \textless{} .001). This is a rather large effect size
(according to the criteria set by Cohen, 1988; see also Bergmann, et
al., 2018; for comparative meta-analytic effect sizes in language
acquisition research). That the effect size is significantly above zero
suggests that when presented with the correctly pronounced label,
infants fixated the corresponding object. Our analysis of funnel plot
asymmetry, however, found evidence for publication bias, which might
lead to an overestimated effect sizes as smaller, non-significant
results might not be published despite the fact that they should occur
regularly even in well-powered studies. Although the effect size Hedges'
\emph{g} may be overestimated for object identification in response to
correctly pronounced words, the p-curve results and a CI lower bound of
0.67, which is substantially above zero, together suggest that this
result is somewhat robust. In other words, we are confident that the
true population mean lies above zero for object recognition of correctly
pronounced words.

@@

@@

The above two analyses considered the data from mispronounced and
correctly pronounced words separately. To evaluate mispronunciation
sensitivity, we compared the effect size Hedges' \emph{g} for correct
pronunciations with mispronunciations directly. To this end, we combined
the two datasets. The moderator test was significant, QM(1) = 215.761,
\emph{p} \textless{} .001. The estimate for mispronunciation sensitivity
was 0.495 (SE = 0.034), and infants' looking times across conditions
were significantly different (CI {[}0.429, 0.561{]}, \emph{p}
\textless{} .001). This confirms that although infants fixate the
correct object for both correct pronunciations and mispronunciations,
the observed fixations to target (as measured by the effect sizes) were
significantly greater for correct pronunciations. In other words, we
observe a significant difference between the two conditions and can now
quantify the modulation of fixation behavior in terms of standardized
effect sizes and their variance. This first result has both theoretical
and practical implications, as we can now reason about the amount of
perturbance caused by mispronunciations and can plan future studies to
further investigate this effect with suitable power.

@@

To evaluate the different predictions we laid out in the introduction
for how mispronunciation sensitivity will change as infants develop, we
next added the moderator age (centered; continuous and measured in days
but transformed into months for ease of interpreting estimates by
dividing by 30.44 for Figure 3).

In the first analyses, we investigate the impact of age separately on
conditions where words were either pronounced correctly or not. Age did
not significantly modulate object identification in response to
correctly pronounced (QM(1) = 0.678, \emph{p} = 0.41) or mispronounced
words (QM(1) = 1.715, \emph{p} = 0.19). The lack of a significant
modulation together with the small estimates (correct: \(\beta\) =
0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p} = 0.41;
mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.007,
0.037{]}, \emph{p} = 0.19) indicates that there was no relationship
between age and target looks in response to a correctly pronounced or
mispronounced label. We plot both object recognition and
mispronunciation sensitivity as a function of age in Figure 3.

We then examined the interaction between age and mispronunciation
sensitivity (correct vs.~mispronounced words) in our whole dataset. The
moderator test was significant (QM(3) = 218.621, \emph{p} \textless{}
.001). The interaction between age and mispronunciation sensitivity,
however, was not significant (\(\beta\) = 0.003, SE = 0.008, 95\%
CI{[}-0.012, 0.018{]}, \emph{p} = 0.731); the moderator test was mainly
driven by the difference between conditions. The small estimate, as well
as inspection of Figure 2 suggests that as infants age, their
mispronunciation sensitivity remains the same.

{[}Christina{]} Can you try and align the axes for both plots?
{[}Katie{]} I can, but then the dotted line doesn't extend the full way
(which I think is quite ugly). Not sure how to fix that.

@@

Of the 32 papers included in the meta-analysis, 13 analyzed the
relationship between vocabulary scores and object recognition for
correct pronunciations and mispronunciations (comprehension = 11 papers
and 39 records; production = 3 papers and 20 records). There is reason
to believe that production data are different from comprehension data
(the former being easier to estimate for parents in the typical
questionnaire-based assessment; Tomasello \& Mervis, 1994), and we
therefore planned to analyze these two types of vocabulary measurement
separately. However, because only 3 papers reported correlations with
productive vocabulary scores, only limited conclusions that can be
drawn. In our vocabulary analysis, we therefore focus exclusively on the
relationship between comprehension and mispronunciation sensitivity.

{[}Katie: Tomasello reference -
\url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1540-5834.1994.tb00186.x}{]}

We first considered the relationship between vocabulary and object
recognition for correct pronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 9 of 10 experimental conditions, with correlation
values ranging from -0.16 to 0.48. The mean effect size Pearson's
\emph{r} of 0.14 was small but did differ significantly from zero (CI
{[}0.03; 0.25{]} \emph{p} = 0.012). However, the lower bound of the CI
is close to zero and considering the small sample size, one might
hypothesize that with more power the small relationship might become
even larger. As a result, we can draw a tentative conclusion that there
is a positive relationship between comprehension scores and object
recognition in response to correct pronunciations.

{[}Christina{]} It's significant now! {[}Katie{]} Must be because you
removed the outliers. I've changed around the wording :)

We next considered the relationship between vocabulary and object
recognition for mispronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 17 of 29 experimental conditions, with correlation
values ranging from -0.35 to 0.57. The mean effect size Pearson's
\emph{r} of 0.05 was small and did not differ significantly from zero
(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). The small correlation and large
variances suggest a lack of relationship between vocabulary and object
recognition for mispronunciations. We again emphasize that we cannot
draw a firm conclusion due to the small number of studies we were able
to include here.

Figure 4 plots the year of publication for all the mispronunciation
sensitivity studies included in this meta-analysis. This figure
illustrates two things: the growing number of mispronunciation
sensitivity studies and the waning number of studies measuring
vocabulary. The lack of evidence for a relationship between
mispronunciation sensitivity and vocabulary size in early studies may
have contributed to increasingly fewer researchers including vocabulary
measurements in their mispronunciation sensitivity experimental design.
This may explain our underpowered analysis of the relationship between
mispronunciation sensitivity and vocabulary size.

@@

@@

In a typical trial in a mispronunciation sensitivity study, the
target-distractor image pairs are first presented in silence, followed
by auditory presentation of a carrier phrase or isolated presentation of
the target word (correctly pronounced or mispronounced). When designing
mispronunciation sensitivity studies, experimenters can choose the
length of time each trial is presented. This includes both the length of
time before the target object is named (pre-naming phase) as well as
after (post-naming phase) and is determined prior to data collection. To
examine the size of the time window analyzed in the post-naming phase,
we must first consider overall length of time post-naming, because it
limits the overall time window available to analyze and might thus
predict which time window was analyzed. Across papers, actual
post-naming phase length varied from 2000 to 9000 ms, with a median
value of 3500 ms. We note that the most popular actual post-naming phase
length was 4000 ms, used in \emph{n} = 74 experimental conditions. There
was an inverse relationship between infant age and actual post-naming
phase length, such that younger infants were presented with longer a
longer post-naming phase, although this correlation was not significant
(\emph{r} = 0.01, \emph{p} = 0.882). Presumably, younger infants may be
exposed to longer trials because their word recognition abilities are
expected to be slower than older infants (Fernald et al., 1998).

Unlike the actual post-naming phase length, the size of the post-naming
time window analyzed can be chosen after the experimental data is
collected. Interestingly, half of the experimental conditions were
analyzed using the same length of post-naming phase as the infant heard
in the actual experiment (124), while the other half were analyzed using
a shorter length of post-naming phase, excluding later portions of the
post-naming phase (127). Across papers, the length of the post-naming
phase analyzed varied from 1510 to 4000 ms, with a median value of 2500
ms. We note that the most popular actual post-naming phase length was
2000 ms, used in \emph{n} = 97 experimental conditions. Similar to
actual post-naming phase length, there was an inverse relationship
between infant age and the size of the post-naming time window analyzed,
such that younger infants' looking times were analyzed using a longer
post-naming time window, here the relationship was significant (\emph{r}
= -0.23, \emph{p} \textless{} .001). Again, the choice to analyze a
shorter post-naming time window is likely related to evidence that speed
of processing is slower in younger infants (Fernald et al., 1998). To
summarize, we observe variation in time-related aspects related to
infants' age. This variation is most pronounced, and even significant,
for the time window that is being analyzed after the target label has
been heard.
